Adaptive Sequential Model Selection

### 2015-07-19 paper.tex

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline\\
 Step& Predictor& Naive pvalue& Saturated pvalue& Max-t pvalue\cr
  \hline\\
1 & 3& 0.00 & 0.00 & 0.00 \\ 
  2 & 9 & 0.00 & 0.00 & 0.00 \\ 
  3 & 4 & 0.00 & \color{red}{0.05} & 0.00 \\ 
  4 & 20 & 0.00 & 0.33 & 0.01 \\ 
  5 & 37 & 0.00 & 0.76 & 0.05 \\ 
  6 & 7 & 0.00 & 0.25 & 0.05 \\ 
  7 & 2 & 0.00 & 0.00 & 0.00 \\ 
  8 & 19 & 0.02 & 0.03 & \color{red}{0.37} \\ 
  9 & 11 & 0.11 & 0.55 & 0.95 \\ 
  10 & 52 & 0.21 & 0.91 & 0.92 \\ 
  11 & 57 & 0.05 & 0.37 & 0.21 \\ 
  12 & 24 & 0.22 & 0.15 & 0.00 \\ 
  13 & 5 & 0.18 & 0.07 & 0.10 \\ 
  14 & 49 & 0.16 & 0.97 & 0.75 \\ 
  15 & 30& 0.21 & 0.15 & 0.05 \\ 
  16 & 46 & \color{red}{0.16} & 0.05 & 0.53 \\ 
  17 & 59 & 0.27 & 0.45 & 0.68 \\ 
  18 & 33 & 0.12 & 0.71 & 0.80 \\ 
  19 & 62 & 0.08 & 0.40 & 0.48 \\ 
  20 & 27 & 0.17 & 0.60 & 0.50 \\ 
   \hline\\
\end{tabular}
\caption[tab:diab]{\em Forward stepwise regression for the diabetes data: naive p-values from forward stepwise regression, 
p-values from the ``saturated'' model, and the ``max-t'' p-values that are presented in this paper. The red annotation indicates the stopping step
prescribed by {\tt forwardStop}. For the max-t p-values, this gives exact FDR control at the 10\% level.}
\label{tab:diab}
\end{table}
The table shows the naive p-values from forward stepwise regression, that do not account for the selection, as well as the
p-values from the ``saturated'' model, and the ``max-t'' p-values that are presented in this paper.
The latter two sets of p-values test someone different hypotheses:  the p-values from the saturated model test whether the partial regression of the predictor just added is zero,
what we call the ``incremental null''
In contrast, the max-t pvalues test whether the current model is adequate, that is, all predictors not in the model  have coefficients equal to zero,
the ``complete null''. (The issue of what hypothesis to test is discussed in section \ref{sec:whichnull}.)
Now it turns out that the max-t test is often more powerful that the saturated model test, and importantly, the max-t pvalues are exactly
independent after we reach the point the model sequence when the complete null is true. This independence means that we can apply
sequential FDR exact stopping rules, such as ``forwardStop'' (\citet{gsell2013sequential}). When applied to the max-t pvalues at FDR 0.10, {\tt forwardStop}
suggested stopping at step 8. In constant, the saturated lvalues gave stopping a point of 3, with no guarantee of FDR control
due to the lack of independence of the p-values.

>>>>

\begin{table}[ht]
\centering
\input{tables/diabetes_edit.tex}
\caption[tab:diab]{\em Forward stepwise regression for the diabetes data: naive p-values from forward stepwise regression, 
p-values from the ``saturated'' model, and the ``max-T'' p-values (computed without knowing $\sigma^2$) that are presented in this paper. The red annotation indicates the stopping step
prescribed by {\tt forwardStop}. For the max-T p-values, this stopping rule gives exact $\text{FDR}_{\text{model}}$ control at the 10\% level.}
\label{tab:diab}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
  \hline\\
 Step& Predictor& Naive pvalue& Saturated pvalue& Max-t pvalue\cr
  \hline\\
1 & 3& 0.00 & 0.00 & 0.00 \\ 
  2 & 9 & 0.00 & 0.00 & 0.00 \\ 
  3 & 4 & 0.00 & \color{red}{0.05} & 0.00 \\ 
  4 & 20 & 0.00 & 0.33 & 0.01 \\ 
  5 & 37 & 0.00 & 0.76 & 0.05 \\ 
  6 & 7 & 0.00 & 0.25 & 0.05 \\ 
  7 & 2 & 0.00 & 0.00 & 0.00 \\ 
  8 & 19 & 0.02 & 0.03 & \color{red}{0.37} \\ 
  9 & 11 & 0.11 & 0.55 & 0.95 \\ 
  10 & 52 & 0.21 & 0.91 & 0.92 \\ 
  11 & 57 & 0.05 & 0.37 & 0.21 \\ 
  12 & 24 & 0.22 & 0.15 & 0.00 \\ 
  13 & 5 & 0.18 & 0.07 & 0.10 \\ 
  14 & 49 & 0.16 & 0.97 & 0.75 \\ 
  15 & 30& 0.21 & 0.15 & 0.05 \\ 
  16 & 46 & \color{red}{0.16} & 0.05 & 0.53 \\ 
  17 & 59 & 0.27 & 0.45 & 0.68 \\ 
  18 & 33 & 0.12 & 0.71 & 0.80 \\ 
  19 & 62 & 0.08 & 0.40 & 0.48 \\ 
  20 & 27 & 0.17 & 0.60 & 0.50 \\ 
   \hline\\
\end{tabular}
\caption{Rob's data}
\end{table}

The table shows the naive p-values from forward stepwise regression, that do not account for the selection, as well as the
p-values from the ``saturated'' model, and the ``max-t'' p-values that are presented in this paper.
The latter two sets of p-values test someone different hypotheses:  the p-values from the saturated model test whether the partial regression of the predictor just added is zero,
what we call the ``incremental null''
In contrast, the max-t pvalues test whether the current model is adequate, that is, all predictors not in the model  have coefficients equal to zero,
the ``complete null''. (The issue of what hypothesis to test is discussed in section \ref{sec:whichnull}.)
Now it turns out that the max-t test is often more powerful that the saturated model test, and importantly, the max-t pvalues are exactly
independent after we reach the point the model sequence when the complete null is true. This independence means that we can apply
sequential FDR exact stopping rules, such as ``forwardStop'' (\citet{gsell2013sequential}). When applied to the max-t pvalues at FDR 0.10, {\tt forwardStop}
suggested stopping at step 8. In constant, the saturated lvalues gave stopping a point of 3, with no guarantee of FDR control
due to the lack of independence of the p-values.
